---
title: "Lab 6 Intro"
date: "`r Sys.Date()`"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library("jpeg")
```

## Setup
1. Login to the lab computer (please don't use your personal computer).  
2. Navigate to github.com and login.   
2. Use GitHub desktop to clone your repository to the desktop.   
5. Copy the class repository to the desktop (https://github.com/jmledford3115/datascibiol).  
6. Copy the files for today's lab from the class repository and paste them into **your** repository.  
7. Open today's lab in RStudio.  

## Review from last time
### *With a partner, discuss the following questions*
1. What is a pipe? Why are they useful in R?
A pipe looks like this: %>%. A pipe allows you to do a sequence of operations on a data frame. 

2. What is the shortcut for making a pipe?
shift+command+m

3. What is the difference between `select`, `filter`, and `mutate`?
Select looks at a column and picks out variables.
Filter looks at a row and picks out observations.
Mutate allows you to add new variables and manipulate the data.

4. What are the logistics of midterm 1?


### Warm-up
1. Open the data `ecs21351-sup-0003-SupplementS1.csv`

```{r}
library(tidyverse)
library(janitor)
```
```{r}
ecosphere <- read_csv("data/ecs21351-sup-0003-SupplementS1.csv", skip=2)
```
```{r}
names(ecosphere)
```

2. Clean the names of the variables

```{r}
ecosphere <- janitor::clean_names(ecosphere)
```

3. Explore the data using a function of your choice

```{r}
glimpse(ecosphere)
```
```{r}
summary(ecosphere)
```

4. Are there more veggie, omni, insecivore, or nectar feeders in the data?
There are more insectivore feeders in the data. 
```{r}
veggie_feeder <- select(ecosphere, diet) %>% 
  filter(diet=="Vegetation")
```

```{r}
omni_feeder <- select(ecosphere, diet) %>% 
  filter(diet=="Omnivore")
```

```{r}
insectivore_feeder <- select(ecosphere, diet) %>% 
  filter(diet=="Invertebrates")
```


5. Which families are Veggie?
Anatidae, Phasianidae, Tetraodonidae, Rallidae are the families that eat vegetation. There are 31 combined. 
```{r}
veggie_families <- select(ecosphere, family, diet) %>% 
  filter(diet=="Vegetation")
veggie_families
```